---
title: "CIA2_MLA2"
author: "Nitya"
date: "2023-12-06"
output:
  pdf_document: default
  html_document: default
---

# Import necessary libraries

```{r}
# Importing relevant libraries
library(arules)
library(arulesViz)
library(dplyr)
library(ggplot2)
library(wordcloud2)
```


# Step 1: Data Loading and Exploration

# Load the dataset

```{r}
medx <- read.csv("C:\\Users\\nitya\\Desktop\\Notes\\T5\\MLA-II\\CIA2\\data22.csv", header = TRUE)
```

# Display the first few rows of the dataset

```{r}
head(medx)
```

# Display summary statistics of the dataset

```{r}
summary(medx)
```

# Check the structure of the dataset

```{r}
str(medx)
```

# Display the dimensions of the dataset

```{r}
dim(medx)
```


# Step 2: Data Transformation for Apriori Algorithm

# Split the dataset into transactions based on "Bill.No."

```{r}
medx_trans <- split(x = medx[,"Item_Code"], f = medx$Bill.No.)
```

# Convert the transactions to the appropriate format

```{r}
medx_trans <- as(medx_trans, "transactions")
```

# Display summary statistics of the transaction data

```{r}
summary(medx_trans)
```

# Visualize item frequency using a bar plot

```{r}
itemFrequencyPlot(medx_trans, topN = 10, type = "absolute")
```


# Step 3: Apriori Algorithm

# Apply the Apriori algorithm with specified parameters

```{r}
apriori_rules <- apriori(medx_trans, parameter = list(sup = 0.001, conf = 0.6, target = "rules"))
```


# Display summary statistics of the generated rules

```{r}
summary(apriori_rules)
```


# Step 4: Rule Inspection and Sorting

# Inspect and display the rules, sorted by lift in descending order

```{r}
inspect(sort(apriori_rules, by = "confidence", decreasing = TRUE))
```


# Step 5: Rule Visualization

# Visualize a subset of rules using a graph

```{r}
plot(head(sort(apriori_rules, by = "confidence")), method = "graph")
```

# Visualize all rules in a grouped manner

```{r}
plot(apriori_rules, method = "grouped")
```